Impact of Demographics and Skills of the Observer on Visual Statistical Inference

### 2013-05-25 sociology_paper.tex
demograpic information figure added

@@

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=3.5in]{reasoning_words.pdf} 
   \caption{Words used to explain the reasons for selection of data plot in a lineup show what features of a lineup may influence a non-statistician to examine it. Larger font indicate more people choosing that word. Different color is used just to separate the words.}
   \label{fig:wordle}
\end{figure}

>>>>

%\begin{figure}[htbp] 
%   \centering
%   \includegraphics[width=3.5in]{age_study_country_bar.pdf} 
%   \caption{Countrywise distribution of education level of the MTurk workers participating the experiments. The spike in graduate degree in India may be due to their consideration of undergraduate degree to be graduate degree as well.}
%   \label{fig:country_study}
%\end{figure}

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{demographic_info.pdf} 
   \caption{Countrywise distribution of age levels of the MTurk workers participating the experiments.}
   \label{fig:age_study}
\end{figure}

@@

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=3.5in]{reasoning_words.pdf} 
   \caption{Words used to explain the reasons for selection of data plot in a lineup show what features of a lineup may help a non-statistician to evaluate it. Larger font indicate more people choosing that word. Different color is used just to separate the words.}
   \label{fig:wordle}
\end{figure}
